Efficient Community Formation \\ for Web Services

### 2014-01-20 papers/coalition-journal-R1/response_letter-final.tex

\vspace{0.2cm}\textbf{\underline{Answer 1}: As argued in our
Answer 2 to Reviewer 1, we are advocating the idea of community as
a way to group web services in order to increase the total gain of
all the members where each web service gain is more than or equal
to what this web service would obtain being outside the community.
This is because the community can provide wider visibility, better
market share, higher reputation, and better way of sharing
resources. Community for us is an infrastructure and being part of
it should benefit the web service, but also the community as a
whole. As argued in [Maamar et al., 2011]\footnote{Z. Maamar, P.
Thiran, and J. Bentahar (2011). Web services communities: from
intra-community Coopetition to inter-community Competition. In
E-Business Application for Product Development and Competitive
Growth: Emerging Technologies, In Lee editor, pp. 333-343, IGI
Global.}, inside a community, web services can either compete or
cooperate. In this paper, we stress the intra-community
cooperation between web services for a better inter-community
competition. The main idea is that to form a stable web service
community and to have fair distribution of the total gain based on
the contribution of each individual, cooperative game theory,
particularly coalition game theory, is very suitable to formalize
such a problem. Cooperation between competitors is a well
established practice in economical theories (see for instance
[Chetty and Wilson 2003]\footnote{S. K. Chetty and H. I. M. Wilson
(2003). Collaborating with competitors to acquire resources.
International Business Review, vol. 12. pp. 61-81.} and [Bucklin
and Sengupta 1993]\footnote{L. P. Bucklin and S. Sengupta (1993).
Organizing successful co-marketing alliances. Journal of
Marketing. vol. 57, pp. 32-46.}). This happens in real business
world scenarios. As an example, let us consider major carrier
airlines providing ticket selling services. Those airlines can be
seen as competing agents, each one tries to maximize its utility
by gaining more market share. However, nowadays those companies
are usually part of different coalitions (alliances) such as Star
Alliance\footnote{\url{www.staralliance.com}} (28 airline members
including Scandinavian Airlines, Thai Airways International, Air
Canada, Lufthansa, and United Airlines),
SkyTeam\footnote{\url{www.skyteam.com}} (19 members, among them
Aerom\'{e}xico, Air France, Delta Air Lines, Continental Airlines,
KLM, and Northwest Airlines), and Oneworld\footnote{\url{
www.oneworld.com}} (13 members including Air Berlin, American
Airlines, British Airways, Cathay Pacific, Iberia, Japan Airlines,
Malaysia Airlines, and Qatar Airways). By sharing resources and
market share and having the option of service multi-hop air
tickets combined from different airlines, each airline member of a
coalition can increase its gain by collaborating. The question is
when this collaboration would be beneficial for all the agents
involved? For example the three alliances would not gain anything
by collaborating and sharing resources with airlines of low
reputation and quality. They will lose their market and would
rather stay away from this collaboration. Therefore, no stable
community can be formed between well established and poor
airlines. Another example of cooperation among competitors is the
arrangement between PSA Peugeot Citro\"{e}n and Toyota to create
Toyota Peugeot Citro\"{e}n Automobile
(TPCA)\footnote{\url{www.tpca.cz/en/}} in order to share
components for a new city car where the different companies save
money on shared costs while remaining competitive in other areas.
Our solution of cooperation between competitor web services within
coalitions follows these models. We updated the paper to reflect
this important discussion by adding a new part, called
motivations, to the introduction (Section 1).}

\vspace{0.5cm}\textbf{\underline{2. Reviewer}:}  First, the
concept of service community used in this paper is different from
the ones used in the existing work, such as in the referred
papers. The general idea of service community is a homogeneous
service group that conceptually include services providing similar
functionality. Services in the same community are independent and
autonomous. There is no central control mechanism for the
community. On the other hand, the concept of service community of
this paper is a group of services which are monitored and managed
by a community manager. It is not clear how realistic or practical
such a community is and what the real world examples are.

\vspace{0.2cm}\textbf{\underline{Answer 2}: Most of the existing
work have clearly stated that communities of web services need a
centralized manager for the purposes of developing, coordinating
and managing the community infrastructure and in some of the
works, being the access point of the community and having the role
of delegating tasks:
%
\begin{itemize}
%
\item {[Liu et al. 2012][28]} (published in the same journal IEEE
Transactions on Services Computing, 2012): The authors used a very
similar architecture to the one we are using in our paper. Each
web service community has a \emph{coordinator} which is
responsible for receiving and satisfying customers' requests and
``\underline{managing the cooperation among the members}''. The
coordinator plays then the role of the community manager.
%
\item {[Lim et al. 2012][26]}: The paper uses exactly the
architecture we are using here. Each community is managed by a
\emph{Master Web Service}.
%
\item {[Benatallah et al. 2003][9]}: The paper introduces the
concept of \emph{service container}, which plays the role of
community and its manager at the same time.  A container is a
service that aggregates several functionally similar services.
Containers exist independently of the services they aggregate. The
service container is the one to invoke instead of an elementary or
composite service aggregated by that container.
%
\item {[Maamar et al. 2008][14], [Maamar et al. 2009][8]}: Here
again the architecture proposed in these papers is the one we are
using in our work.
%
\item {[Zeng et al. 2003][11]}: The paper describes a global
planning selection algorithm and a delegation algorithm to be run
when a request to execute an operation is received by the
community. This needs a central entity to run those algorithms.
Such entity plays the role of the community coordinator or
manager.
%
\item {[Medjahed and Bouguettaya 2005][13]}: The paper describes
the concept of \emph{community agents} associated to
\emph{community providers}. A community agent is responsible,
among other things, of the registration of services with the
community. The paper uses the example of a community that provides
health care services to senior citizens. In this example, a
governmental entity is needed to check the health care standards
used by the members before authorizing them to be part of the
community. Such a central entity is represented by the community
agent. Thus, community agents are playing the role of community
managers.
%
\item {[Limam and Akaichi 2010]}\footnote{H. Limam and J. Akaich.
Managing web services communities: A cache for queries
optimisation, International Journal on Web Service Computing,
Vol.1, No.1, pp 2230-7702, 2010}: The paper describes explicitly
the concept of \emph{centralized access} in the community
definition.
%
\end{itemize}
%
It is worth mentioning that in our work, service community is also
a homogeneous service group that hosts services providing similar
functionalities. Moreover, services in the same community are also
independent and autonomous in our work. They are self-interest and
utility maximizer agents, and behave autonomously towards
maximizing their own profits using our game theory approach. They
have the freedom to leave the community anytime if they are not
satisfied about the profit they are making. Having a community
manager, only means that the management of the community
infrastructure in terms of accepting new web services and
verifying the credentials of the members is centralized. In other
words, the coordinator does not manage web services, but does
manage the community. The manager does not dictate what the web
services should do and how they should behave. In fact, all the
existing proposals agree that because the community is an
infrastructure that hosts different web services, membership
cannot be leaved open so that any web service can join even those
having poor quality and bad reputation. A community is a system
that should accept only particular web services, and there should
be a mechanism to control the credentials of the members.}

\textbf{Going back to the real world example of airlines
alliances:
%
\begin{itemize}
%
\item Star Alliance is managed by a centralized company \emph{Star
Alliance Services GmbH}, which was created on behalf of its
members and led by the current CEO, Mark Schwab. Star Alliance
Services GmbH is responsible of coordinating the development and
strategies of the airline alliance from its base in Frankfurt am
Main,
Germany\footnote{\url{www.staralliance.com/en/about/organisation/}}.
%
\item SkyTeam has centralized core management team, \emph{SkyTeam
Central}, based at the World Trade Center Schiphol Airport and led
by the current Chairman of the SkyTeam Governing Board, Leo van
Wijk. The core management team ``is responsible for overseeing
day-to-day operations of the alliance, including: marketing,
sales, airport synergies and transfer product, cargo, advertising
and brand, alliance operations, finance, corporate communications
and alliance
administration''\footnote{\url{http://www.skyteam.com/en/About-us/Organization/Management/}}.
%
\item Oneworld is managed by its central alliance office, the
\emph{Oneworld Management Company} (\emph{oMC}) based in New York
City and led by Tom Horton (Chairman) and Bruce Ashby (CEO). The
oMC acts as the alliance's central secretariat, with
responsibility for driving future growth and the launch of new
customer services and
benefits\footnote{\url{www.oneworld.com/news-information/oneworld-fact-sheets}}.
%
\end{itemize}
%
In all these alliances, accepting a new member or pending a member
is decided centrally. Regarding the second example, TPCA coalition
is also managed by a central management company based in the
industrial zone of Kolin - Ov\v{c}\'{a}ry, Czech republic and led
by Kenta Koide,
president\footnote{\url{www.tpca.cz/en/about-us/management-tpca-en-us/}}.}
%

\textbf{In the revised manuscript, we reported these discussions
in the motivation part of the introduction (Section 1) and in the
related work section (Section 2).}

\vspace{0.5cm}\textbf{\underline{3. Reviewer}:}  The problem is
modeled in a way so that the cooperative game theory can be
applied, but not in a way that is consistent with the real world
scenarios.

\vspace{0.2cm}\textbf{\underline{Answer 3}: Answers 1 and 2 are
answers for this comment as well.}

\vspace{0.5cm}\textbf{\underline{4. Reviewer}:}  The service
parameters, such as its request rate and  throughput rate are not
in line with the general characteristics of web services, such as
input and output parameters. It is not clear how the proposed
service parameters are obtained and why they are important to
determine a service's membership to a community, considering that
they depend on not only the service's capacity, but also the
amount and frequency of user requests, which can be random.

\vspace{0.2cm}\textbf{\underline{Answer 4}: First, we have to
mention that we are focusing on \underline{quality metrics}, which
are non-functional. Our proposal is general and independent from
the functional input-output parameters. The parameters we are
using are the typical parameters of web services,  which are
obtained from a real world data set provided at:
\url{http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/}. The
request rate was inspired by market share and reputation models of
communities of web services, which have been used in other
proposals such as [17],[23]. Those parameters are important as
community coordinators tend to accept only good web services which
provide good QoS and have the potential to increase the utility of
the community. It has been showed in [23] that the request rate is
positively correlated with the trust and performance of web
services, which means it is not random when the service is running
for a large enough period of time. In fact, having a
\emph{casi-static} request rate for communities is not
unrealistic. To support our claim, we provide data from a real
world example. The CEO of \url{concertboom.com}, Kooshiar Azimian,
has provided us with their access and request rates of the web
services they use\ref{cblog}. Their service provides ticketing
information for events happening close to user's location. They
use Ticketnetwork.com web services\footnote{Affiliate program
link: http://www.ticketnetwork.com/affiliates/agreement.aspx}
\footnote{Web Service API documentation:
\url{www.getacoder.com/data/projects/77613/TicketNetwork\%20Web\%20Services\%20(W2)-.doc}},
and have implemented their back-end code in Java. As shown in
Figure \ref{fig1}, they currently have an average of 340,000 daily
page views or almost 3.95 requests per second. They invoke the
\url{ticketnetwork} web service almost 4 times per second to get
the seating chart and tickets available for the events. During a
day, the pick time happens at around 20:00 UTC time, which has
almost 10\% more requests than during the lower pick time, which
happens around 7:00 AM UTC time. As shown in the figure, the
pattern of request rate is casi-stable during the period between
May and September.
%Therefore, \url{ticketnetwork} knows that
%\url{concertboom.com} has a request rate of 340,000 requests per
%day or almost 3.95 requests per second and can adjust the internal
%service providers and resources so they can  provide these rate of
%services.
}

\textbf{Because the data of \url{concertboom.com} are private, we
were asked not to disclose them publicly. We only get from the
company the consensus to use them for the response letter. This is
the reason why we could not add them to the paper.}

\begin{figure}
\begin{center}
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=10cm]{cb.eps}\label{cblog}
\caption{Number of ticket pageviews of concertboom.com during May 5th, until Sep 9th, 2013}
\label{fig1}
\end{center}
\end{figure}

\vspace{0.5cm}\textbf{\underline{5. Reviewer}:}  The paper
conducted a simulation instead of an experimental study using real
world web services. This also suggests the difficulties of finding
real world examples and application for the proposed idea.

\vspace{0.2cm}\textbf{\underline{Answer 5}:
%Our focus is on non-functional properties of web services and is extendable to any type of web service communities providing any type of service, which there is high demand, request load and competition for that service type such as mapping, weather, ticketing, and local places information.
As mentioned previously, for our experiments, we have implemented
our web services using real data extracted from a data set of web
services
(\url{http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/}).
This makes our web services behave like real ones. In the previous
version, web services were implemented as abstract enteties as the
main purpose was to focus on the quality metrics. In the revised
version, we use flight booking services and airlines coalitions as
concrete application domain. An XML SOAP based messaging system is
also implemented. The request contains the flight dates, the
origin and destination, type of tickets, and number of guests. The
response contains different flights with different companies,
prices, timing, etc. We have gathered around 200,000 flights and
stored them in our MongoDB database. As expected, this did not
affect our experimental results, since our concern, as most of the
related work, is on non-functional properties of web services. We
could deploy web services using JAX-WS in Java and deploy on
different servers. However, those web services would not reflect
the quality of service parameters of real web services under load
in real world. For example, we cannot evaluate the exact
bottlenecks different type of services may have, some qualities
may drop because of heavy load of DB queries, some because of
network congestions and delays while trying to generate the
results for end users. Therefore, the real world data can provide
us with QoS values of real functioning web services online. We
have carefully examined many published proposals in services
computing including work on web service community and composition
such as [Yu 2013]\footnote{Q. Yu and A. Bouguettaya, Efficient
Service Skyline Computation for Composite Service Selection, IEEE
Transactions on Knowledge and Data Engineering (TKDE), vo. 25, no.
4, pp. 776-789, 2013}, [Limam 2010]\footnote{H. Limam and J.
Akaich. Managing web services communities: A cache for queries
optimisation, International Journal on Web Service Computing,
Vol.1, No.1, pp 2230-7702, 2010}, [Liu 2012]\footnote{A. Liu, Q.
Li, L. Huang, S. Ying, and M. Xiao,Coalitional game for
community-based autonomous web services cooperation, IEEE
Transactions on Services Computing, vol. 99, no. PrePrints, 2012.}
and many others; we found that they evaluated their results using
a similar methodology. For the real world applications part of the
comment, see the previous answers.}

\vspace{0.5cm}

\vspace{1cm}

{
%\bibliographystyle{plain}
%\bibliography{omar}
}
\end{document}
